\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3.6cm}

\firstname{Richard Jason}
\familyname{Peasgood}

%%\address{268 Phillip St}{Waterloo, On N2L 6G9}
\mobile{(519) 721 7878}
\email{jpeasgood@gmail.com}

\begin{document}

\makecvtitle

\section{Education}

\cventry{Jan 2010 -- Nov 2014}{Ph.D. Candidate in Computer Science}{University of Waterloo}{Waterloo, Ontario, Canada}{}{Supervisor: Prof. George Labahn \newline All But Degree. Research was on continuing work extending ideas from my Master's Thesis on integral transforms of holonomic functions.}
\cventry{Sept 2006 -- Dec 2009}{Master of Mathematics in Computer Science}{University of Waterloo}{Waterloo, Ontario, Canada}{}{Supervisor: Prof. George Labahn \newline Thesis: Implicitly Calculating Integral Transforms of Holonomic Functions with Holonomic Kernels.}
\cventry{Sept 2002 -- May 2006}{Bachelor of Science}{University of Manitoba}{Winnipeg, Manitoba, Canada}{}{Joint Honours Computer Science and Mathematics}

\section{Programming Languages}

\cvitem{}{Fluent: C++, Maple\newline Familiar: C, C\#, Java, SQL, Python, MATLAB, Mathematica, JavaScript, HTML, CSS}

\section{Experience}

\subsection{Vocational}

\cventry{Sept 2009 - Dec 2009}{MITACS ACCELERATE Internship Program}{Maplesoft}{Waterloo, Ontario, Canada}{}{Implemented algorithms from my Master's Thesis into the Maple computer algebra system.}

\cventry{May 2005 -- Sept 2006}{Programmer Analyst}{Manitoba Hydro}{Winnipeg, Manitoba, Canada}{}{Developed custom solutions using HTML/CSS, JavaScript, ASP, Access/VBA, Visual Basic 6, and SQL for Microsoft SQL Server/Oracle that extended the Cerenade eForms Enterprise Server application.}

\subsection{Teaching}

\cventry{Sept 2009 -- Aug 2014}{Teaching Assistant}{University of Waterloo}{Waterloo}{}{Courses: CS 487/687 - Introduction to Symbolic Computation, CS 330 - Management Information Systems, CS 370 - Numerical Computation., CS 136 - Elementary Algorithm Design and Data Abstraction, CS 200 - Concepts for Advanced Computer Usage, CS 245/SE 212 - Logic and Computation, CS 125 - Intro to Programming, and CS 134 - Intro to Computer Science.}
\cventry{Sept 2004 -- May 2006}{Teaching Assistant}{University of Manitoba}{Winnipeg}{}{Courses: MATH 1300 - Vector Geometry and Linear Algebra and MATH 1200 - Elements of Discrete Mathematics.}

\section{Honours and Awards}

\cventry{2015}{Coop Service Award}{COCHF}{Ontario, Canada}{}{}
\cventry{2012}{QEII -- Graduate Scholarship in Science and Technology}{Ontario, Canada}{}{}{}
\cventry{2006}{Ontario Graduate Scholarship in Science and Technology}{Ontario, Canada}{}{}{}
\cventry{2006}{Graduate Entrance Scholarship}{University of Waterloo}{Waterloo, Ontario, Canada}{}{}
\cventry{2002 -- 2006}{Dean's Honour List}{University of Manitoba}{Winnipeg, Manitoba, Canada}{}{}

\section{Volunteering}

\cventry{Oct 2012 -- Present}{President of the Board of Directors'}{Waterloo Co-operative Residence Incorporated}{Waterloo}{}{Currently sit on the HR committee. Lead major
overhauls to policies that changed the way the Executive Director is monitored
and evaluated. Chaired board meetings, meetings of the membership and the HR
Committee. Oversaw Lawyers and HR consultants on several projects.}
\cventry{Oct 2009 -- Apr 2014}{Executive Member}{University of Waterloo Mambo Club}{Waterloo}{}{Taught and designed salsa dance instruction curriculum for intermediate salsa dancers at UW, organized promotional campaigns, hosted citywide salsa events inviting special guests from Toronto, designed and maintained website for club members.}

\end{document}
